paper_replication

### 2021-12-14 paper_replication.Rmd
Update paper_replication.Rmd

# clean countydem data to make counties and states match those in abortion count data 
countydem <- read.csv("county_demographics.csv")

@@

abortions2010$county <- str_to_title(abortions2010$county)
countydem$county <- str_to_title(countydem$county)

abortions2010$county <- gsub(abortions2010$county, pattern = "[()]", replacement = "")
abortions2010$county <- gsub(abortions2010$county, pattern = "Ind. City", replacement = "City")
abortions2010$county <- gsub(abortions2010$county, pattern = "Saint", replacement = "St.")
abortions2010$county <- gsub(abortions2010$county, pattern = "Miami Dade", replacement = "Miami-Dade")
abortions2010$county <- gsub(abortions2010$county, pattern = "Hawai'i", replacement = "Hawaii")
abortions2010$county <- gsub(abortions2010$county, pattern = "Kaua'i", replacement = "Kauai")
abortions2010$county <- gsub(abortions2010$county, pattern = "St.e Genevieve", replacement = "Ste. Genevieve")
abortions2010$county <- gsub(abortions2010$county, pattern = "Shannon/Oglala Lakota", replacement = "Oglala Lakota")

#Add number of women to abortion count data
for (i in 1:nrow(abortions2010)) {
  if (length(countydem$Women[countydem$state.abb == abortions2010$state[i] & countydem$county == abortions2010$county[i]]) == 0) {
    abortions2010$Women[i] <- NA
  }
  else {
    abortions2010$Women[i] <- countydem$Women[countydem$state.abb == abortions2010$state[i] & countydem$county == abortions2010$county[i]]
  }
}

#fix NA values
abortions2010$X2010 <- na_if(abortions2010$X2010, "?")
abortions2010$X2010 <- na_if(abortions2010$X2010, "")
abortions2010$X2010 <- as.numeric(abortions2010$X2010)

@@

#look at counties missing women pop data
abortions2010missingwomen <- abortions2010[is.na(abortions2010$Women), ]
#DeWitt, Bedford city, Clifton Forge city in abortion rate data  but not county dem data

#calculate abortion rates
abortions2010 <- abortions2010 %>% mutate(rate = X2010/Women)

#Add abortion counts to county data
for (i in 1:nrow(countydem)) {
  if (length(abortions2010$rate[abortions2010$state == countydem$state.abb[i] & abortions2010$county == countydem$county[i]]) == 0) {
    countydem$AbortionRate2010[i] <- NA
  }
  else {
    countydem$AbortionRate2010[i] <- abortions2010$rate[abortions2010$state == countydem$state.abb[i] & abortions2010$county == countydem$county[i]]
  }
}

@@

missingcounties <- countypresdem2008[!(countypresdem2008$county_name %in% countydem$county), ]

@@

countydem <- left_join(countydem, countypresdem2008, by = c("state.abb", "county"))
```

@@

@@

```{r}
#make new variable for high vs. low restrictions
restrictions <- restrictions %>% mutate(totalrestrict = parental_involvement + two_trips + trap + unconstitutional_ban, 
                                        highorlow = case_when(totalrestrict >= 3 ~ "high", 
                                                              totalrestrict < 3 ~ "low"))
```

@@

```{r}
propensitywts <- glm(inanalysis ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008, data=countydem, family=binomial())
summary(propensitywts)

@@

```{r}
countydemanalysis <- df %>% filter(inanalysis == 1)
countydemanalysis <- left_join(countydemanalysis, restrictions, by = "state")
countycentroids <- countycentroids %>% rename(county = COUNAME, state = STNAME)
countycentroids$county <- str_to_title(countycentroids$county)
countycentroids <- countycentroids %>% select(county, state, distancetoprovider)
countydemanalysis <- left_join(countydemanalysis, countycentroids, by = c("state", "county"))

countydemanalysis$highorlow <- factor(countydemanalysis$highorlow, levels = c("low", "high"))
model <- lm(AbortionRate2010 ~ highorlow + distancetoprovider + highorlow*distancetoprovider, data = countydemanalysis, weights = ps)
summary(model)

>>>>

```{r}
########### clean county dem data ###########
countydem <- read.csv("county_demographics.csv")

@@

countydem$county <- str_to_title(countydem$county)

length(unique(abortions2010$state)) #only 42 states in abortion data

#look at percent missing abortion counts by state
aggregate(X2010 ~ state, data = abortions2010, function(x) {sum(!(is.na(x)))/length(x)}, na.action = NULL)

# clean abortion data to make counties and states match county dem data
abortions2010$county <- str_to_title(abortions2010$county)
abortions2010$county <- gsub(abortions2010$county, pattern = "[()]", replacement = "")
abortions2010$county <- gsub(abortions2010$county, pattern = "Ind. City", replacement = "City")
abortions2010$county <- gsub(abortions2010$county, pattern = "Saint", replacement = "St.")
abortions2010$county <- gsub(abortions2010$county, pattern = "Miami Dade", replacement = "Miami-Dade")
abortions2010$county <- gsub(abortions2010$county, pattern = "Hawai'i", replacement = "Hawaii")
abortions2010$county <- gsub(abortions2010$county, pattern = "Kaua'i", replacement = "Kauai")
abortions2010$county <- gsub(abortions2010$county, pattern = "St.e Genevieve", replacement = "Ste. Genevieve")
abortions2010$county <- gsub(abortions2010$county, pattern = "Shannon/Oglala Lakota", replacement = "Oglala Lakota")

#fix NA values and make abortion counts numeric
abortions2010$X2010 <- na_if(abortions2010$X2010, "?")
abortions2010$X2010 <- na_if(abortions2010$X2010, "")
abortions2010$X2010 <- as.numeric(abortions2010$X2010)

@@

#look at counties in abortion data but not countydem data
abortions2010$county[!(abortions2010$county %in% countydem$county)]
#"St. Louis County", "Bedford City", "Clifton Forge City"

#look at counties in countydem data but not abortion data
countydem$county[!(countydem$county %in% abortions2010$county)] #many 
unique(countydem$state.abb[!(countydem$state.abb %in% abortions2010$state)]) #"AK" "CT" "IA" "LA" "MA" "NH" "NM" "WY"

#Add abortion counts to county data
for (i in 1:nrow(countydem)) {
  if (length(abortions2010$X2010[abortions2010$state == countydem$state.abb[i] & abortions2010$county == countydem$county[i]]) == 0) {
    countydem$AbortionCount2010[i] <- NA
  }
  else {
    countydem$AbortionCount2010[i] <- abortions2010$X2010[abortions2010$state == countydem$state.abb[i] & abortions2010$county == countydem$county[i]]
  }
}

#calculate abortion rates
countydem <- countydem %>% mutate(AbortionRate2010 = AbortionCount2010/Women)

#look at percent missing abortion rates by state
aggregate(AbortionRate2010 ~ state, data = countydem, function(x) {sum(!(is.na(x)))/length(x)}, na.action = NULL)

@@

missingcounties <- countypresdem2008[!(countypresdem2008$county_name %in% countydem$county), ] #all of AK and a few others (DC, Dona Ana New Mexico, Kansas City Missouri, Maine Uocava Maine, Federal Precinct Rhode Island)

@@

countydem <- left_join(countydem, countypresdem2008, by = c("state.abb", "county"))

#look at percent missing dem vote by state
aggregate(percentdem2008 ~ state, data = countydem, function(x) {sum(!(is.na(x)))/length(x)}, na.action = NULL)

@@

countycentroids <- countycentroids %>% rename(county = COUNAME, state = STNAME)
countycentroids$county <- str_to_title(countycentroids$county)
countycentroids <- countycentroids %>% select(county, state, distancetoprovider)
countycentroids <- countycentroids %>% filter(state != "Puerto Rico")
countycentroids$county <- gsub(countycentroids$county, pattern = " City", replacement = "")

missingcounties <- countycentroids[!(countycentroids$county %in% countydem$county), ] #Alaska and DC

countydem <- left_join(countydem, countycentroids, by = c("state", "county"))

#look at percent missing distance by state
aggregate(distancetoprovider ~ state, data = countydem, function(x) {sum(!(is.na(x)))/length(x)}, na.action = NULL)

@@

```{r}
#make new variable for high vs. low restrictions
restrictions <- restrictions %>% mutate(totalrestrict = parental_involvement + two_trips + trap + unconstitutional_ban, 
                                        restrictionlevel = case_when(totalrestrict >= 3 ~ "high", 
                                                              totalrestrict < 3 ~ "low"))
restrictions$state[!(restrictions$state %in% countydem$state)] #none
countydem <- left_join(countydem, restrictions, by = "state")
countydem$restrictionlevel <- factor(countydem$restrictionlevel, levels = c("low", "high"))

@@

```{r}
#calculate propensity scores
propensitywts <- glm(inanalysis ~ Black.pct + Native.American.pct + Asian.pct + Hispanic.pct + Median.Income + Women + percentdem2008, data=countydem, family=binomial())
summary(propensitywts)

@@

```{r}
#run models
countydemanalysis <- countydem %>% filter(inanalysis == 1)

model <- lm(AbortionRate2010 ~ restrictionlevel + distancetoprovider + restrictionlevel*distancetoprovider, data = countydemanalysis, weights = ps)
summary(model)
